Analysis of Odd one out experiment

### 2019-06-17 reports/odd_one_out/analysis_oddoneout.Rmd
new prediction of odd scene
- predict human performance
- predict CNN prediction

participants <- readxl::read_excel(here("data","oddoneout","oddoneout_participants.xlsx"))
```

@@

>>>>

df <- df %>% anti_join(wrong_trials, by = c("prot_id_version"="prot_id","trial_id"))

participants <- readxl::read_excel(here("data","oddoneout","oddoneout_participants.xlsx"))

metrics <- readRDS(file = here("data", "oddoneout", "metrics_190614.rds"))
```

@@

## Metrics

```{r}
p <- metrics %>% 
  filter(metric!= "ssim_correct" & metric!= "correct") %>% 
  ggplot(aes(x = quintile, y = value_fc7, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  theme(text = element_text(size=18)) + scale_color_discrete(labels = c("GIST", "HOG", "RGB", "SIFT")) + 
  stat_summary(fun.y=mean, geom="line") +
  ggtitle("Predict CNN")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_explanation_fc7.eps"), p, width = 6, height = 6)

p <- metrics %>% 
  filter(metric!= "ssim_correct") %>% 
  ggplot(aes(x = quintile, y = value_partic, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  theme(text = element_text(size=18)) + scale_color_discrete(labels = c("Humans", "GIST", "HOG", "RGB", "SIFT")) + 
  stat_summary(fun.y=mean, geom="line") +
  ggtitle("Predict human peformance")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman.eps"), p, width = 6, height = 6)
